Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2016-02-08 paper.tex
rephrase paper scope mention

A fleet reactor archetype was created for Cyclus.  Although the modeling of
individual, discrete facilities was a motivation for Cyclus, its flexibility
makes it relatively straightforward to create plug-in archetypes to model
anywhere along the spectrum from individual, discrete facilities to continuous
flow fleet facilities.  In order to contrast well with the individual,
single-facility granularity modeling that is part of the standard Cyclus
archetypes, a fleet archetype was created for this work with aggregate
facility behavior and continuous flow.  Although it would certainly be
interesting to compare many intermediate levels of facility discretization
(e.g., 1-reactor groups, 10-reactor groups, single-fleet, etc.), such a
detailed analysis is beyond the scope of this work.
% address technical comment 14

>>>>

A fleet reactor archetype was created for Cyclus.  Although the modeling of
individual, discrete facilities was a motivation for Cyclus, its flexibility
makes it relatively straightforward to create plug-in archetypes to model
anywhere along the spectrum from individual, discrete facilities to continuous
flow fleet facilities.  In order to contrast well with the individual,
single-facility granularity modeling that is part of the standard Cyclus
archetypes, a fleet archetype was created for this work with aggregate
facility behavior and continuous flow.  Although it would certainly be
interesting to compare many intermediate levels of facility discretization
(e.g., 1-reactor groups, 10-reactor groups, single-fleet, etc.), only the two
extremes of continuous, single fleet and individual reactor modeling are
investigated in order to maintain an appropriate scope.
% address technical comment 14
